A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-31 writeup/paper.tex
small changes

Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
\begin{align}	
	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
%
Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
\end{align}	
where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.

@@

We used Google Translate to translate all 10,000 words for each of the 50 foreign language that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

>>>>

%Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
%\begin{align}	
%	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
%\end{align}	
%where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
%

Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above.

%Quality for a language is then given by
%\begin{align}	
%	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
%\end{align}	
%where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.

@@

We used Google Translate to translate all 10,000 words for 50 foreign languages that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

%We translated: af ar az bg ca cs cy da de el eo es eu fa fi fr gl gu he hr hu hy id is it ja kn ko lt lv ms nl pl pt ro ru sk sl sq sr sv sw ta te th tr uk ur vi zh
